Turbulence in compact to giant HII regions

### 2022-05-18 strucfunc_paper.tex
Add subscripts "obs" and "mod" to B(r)
This is to disambiguate the model and observed structure functions

\newcommand\hii{\ion{H}{2}}
\newcommand\pos{\ensuremath{_{\mathrm{pos}}}}
\newcommand\los{\ensuremath{_{\mathrm{los}}}}
\newcommand\noise{\ensuremath{_{\text{noise}}}}
\newcommand\halpha{H${\alpha}$}
\newcommand\n{[\ion{N}{II}]$\lambda$6584}
\newcommand\oi{[\ion{O}{III}]$\lambda$5007}
\newcommand\s{[\ion{S}{II}]$\lambda$6737}
\newcommand\kms{$^{-1}$}

@@

In order to capture these two behaviors,
We therefore propose the following idealized 2-parameter model
for the autocorrelation function:
%
\begin{equation}\label{eq:new-correlation-form}
  C(r;\ r_0, m) = 2^{- \left( r/r_0 \right)^m} 
\end{equation}
%
in which \(r_{0}\)\ is the correlation length (see above)
and \(m\) is the power-law slope at small scales.
This is constructed so that \(C(r) = 1/2\) at \(r = r_0\),
while the exponential form ensures that \(C(r)\) rapidly approaches zero
for larger separations.
We use equation \eqref{eq:functional} to determine the structure function
from this model autocorrelation function.
The resultant model structure function has the following properties:
\begin{enumerate}[1.]
 \item Small scales: \(B(r) \propto r^m\) for \(r \ll r_0\);
 \item Correlation scale: \(B(r_0) = \sigma\pos^2\);
 \item Large scales: \(B(r) \to 2 \sigma\pos^2\) for \(r \gg r_0\).
 \end{enumerate}
An example is shown by the blue line in Figure~\ref{fig:model-strucfunc}a.

@@

Combining both the effects of seeing and noise yields the corrected
model structure function:
\begin{equation}
  \tilde{B}(r)
  = 
  2\sigma^2\pos \left[
    1 - 2^{- \left( r/r_0 \right)^m} 
  \right]
  \,  S(r) + B\noise
\label{eq:sf-functional}
\end{equation}
An example of this equation is shown by the red line in Figure~\ref{fig:model-strucfunc}.
Note that seeing and noise have opposite effects on the slope
of the structure function at intermediate scales:
seeing tends to steepen the slope, while noise tends to flatten it.
This can lead to a degeneracy between these two parameters
when fitting observations over a limited range of separations.

@@

\begin{table}
  \centering
  \caption{Bounds of allowed values for parameters in model fits}
  \label{tab:parameter-ranges}
  \newlength\partabwidth
  \setlength\partabwidth{0.7\linewidth}
  \begin{tabular*}{\partabwidth}{@{\extracolsep{\fill}}l rr}
    \toprule
    Parameter & Lower & Upper\\
    \midrule
    \(\sigma^2\) & \(0.25\, \max [B]\)& \(2\, \max [B]\)\\
    \(r_0\) & \(0.01\, L\) & \(2\, L\)\\
    \(m\) & \(0.5\) & \(2.0\) \\
    \(s_0\) & \SI{0.1}{arcsec}& \SI{1.5}{arcsec}\\
    \(B\noise\) & \(0\) & \(3\, \min [B]\) \\
    \bottomrule
    \multicolumn{3}{@{}p{\partabwidth}@{}}{
    Note: \(\max[B]\) and \(\min[B]\) are over all bins in the observed structure function.
    }
  \end{tabular*}
\end{table}

@@

In order to provide a uniform description of the velocity fluctuations,
we fit the model structure function
\(\tilde{B}(r)\) of equation~\eqref{eq:sf-functional}
to each \hii{} region in our sample.
Results are shown in Figures~\ref{fig:strucfunc-fit-Galactic}, \ref{fig:strucfunc-fit-MC},
and \ref{fig:strucfunc-fit-ExtraGal}, arranged in order of increasing distance.
Best-fit values for the model parameters,
together with 95\% credibility range,
are given in Table~\ref{tab:Res}.
After describing the methods used to
measure the structure function and fit the model (section~\ref{sec:techn-deta-model}),
we give details of the results in the example case of
the inner Orion Nebula (\ref{sec:example-results-orion})
and a broad overview of the results for other regions (\ref{sec:results-model-fitt}).
Further details of the results for individual regions are
given in Appendix~\ref{sec:notes-individual-hii}.

@@

For the observational values (blue symbols),
the structure function is the average value of equation~\eqref{eq:Br}
over all pairs of points that contribute to each radial bin.
The uncertainty of each bin (blue error bars) is estimated
as the standard deviation of these values divided by the square root of
the number of contributing pairs.
\textit{But this is not true -- we use constant fractional error with adjustments for small and large separations.}
For most sources a fixed bin size of \SI{0.05}{dex} is used,
but for those observed with multi-fiber spectroscopy
(Carina and M8, see section~\ref{sec:flames-multi-fiber}),
where coverage is sparse at small separations,
adjacent bins were merged to ensure at least 100 pairs contribute to each bin.
Bins with separation less than \(L/2\) are used to constrain the model fitting (filled symbols),
while larger separations (open symbols) are not used
since they are more likely to be affected by a breakdown
of the homogeneity assumption (see section~\ref{sec:limit-model-struct}).
%This \(L/2\) constrain is not used for the regions observed with MUSE.

Non-linear weighted least square fitting of the model is performed
using the Levenberg-Marquardt algorithm \citep{More:1978a} as implemented in the
\texttt{lmfit} Python library \citep{newville_matthew_2014_11813}.
The best-fit model \(\tilde{B}(r)\) is shown (heavy orange solid line),
together with the corresponding underlying ``true model'' \(B(r)\) (heavy dashed green line),
which does not include the effects of seeing or noise.
Note that the true model \(B(r)\) depends on only 3 parameters:
\(\sigma^2\), \(r_0\), and \(m\),
whereas \(\tilde{B}(r)\) additionally depends on
the observational nuisance parameters: \(s_0\) and \(B\noise\).
The best-fit values of each of these parameters are shown by
horizontal and vertical lines in the figure and are summarised in Table~\ref{tab:Res}.

The posterior distributions of model parameters
that are consistent with the observations for each region are estimated
using Markov Chain Monte Carlo (MCMC) ensemble sampling \citep{2010CAMCS...5...65G}
as implemented in the \texttt{emcee} Python library \citep{2013PASP..125..306F}.
A uniform prior distribution is assumed between upper and lower bounds
for each parameter, as given in Table~\ref{tab:parameter-ranges}.
To help ensure convergence of the MCMC algorithm,
we used chain lengths that exceeded \num{50} times the
estimated autocorrelation length for each parameter,
which typically required of order \num{50000} samples.
Thin translucent lines in the figures show structure functions using the parameters of
a random selection of \num{100} posterior samples from the MCMC chain,
both for \(\tilde{B}(r)\) orange and \(B(r)\) (green).
This gives an estimate in the uncertainty about the best-fit model.
Credibility intervals for the parameters are estimated from percentiles
of the posterior distribution and are indicated in the figures by shaded gray boxes
around the best-fit parameter values
(heavy shading for 68\% interval; light shading for 95\% interval).
The 95\% credibility interval for each parameter and for each source
is also given in Table~\ref{tab:Res}.
Figure~\ref{fig:corner-example-Orion} gives an example for Orion of
the pairwise correlations in the posterior distributions of the model parameters,
plotted using the \texttt{corner} Python library \citep{2017ascl.soft02002F}.
Corresponding plots for the remaining sources and a table for the fitting parameters are given in Appendix~\ref{sec:addit-covar-corn}.

@@

The structure functions for sources in the Magellanic Clouds are shown in Figure~\ref{fig:strucfunc-fit-MC}
and those in more distant galaxies in Figure~\ref{fig:strucfunc-fit-ExtraGal}.
The Magellanic cloud sources have generally high data quality due to the
large number of independent spatial points in the MUSE observations
(section~\ref{sec:muse-integral-field}).
The relatively poor spectral resolution means that the \(B(r)\) cannot
be measured down to such low values as in the inner Orion Nebula,
but the larger amplitude of the fluctuations in these sources means
that the fitted model parameters are still tightly constrained.

@@

The inner Orion Nebula has the largest inferred seeing FWHM of \SI{2.4(4)}{arcsec},
which is at least two times higher than the typical seeing measured during the observations
\citep{Doi:2004a}.
However, this can be explained by the fact that the velocity map is constructed
by interpolating individual longslit observations onto a regular grid
(section~\ref{sec:longsl-echelle-spect}).
The seeing-limited resolution will only be achieved along the slits,
whereas the resolution in the perpendicular direction is determined by the slit spacing of \SI{2}{arcsec}.
Given, this the model-derived value of \(s_0\) for this source is reasonable.

@@

At scales larger than \(L/2\),
we see a variety of different shapes for the structure functions
of our sample regions. 
In some cases,
such as Carina and Hubble~X,
\(B(r)\) remains flat at a value of \(\approx 2\sigma^2\),
which is consistent with uncorrelated homogeneous fluctuations
at the largest scales.

For other regions,
such as the Orion Nebula (both inner and outer) and 30~Doradus,
there is a clear downturn in \(B(r)\) at the largest separations.
As discussed above in section~\ref{sec:limit-model-struct},
this is what would be expected if the velocity fluctuations
were inhomogeneous, with a larger amplitude in the center of the map
and a smaller amplitude in the outskirts.
A similar behavior, although not so marked, is shown by
Hubble~V and NGC~595.
The Orion Nebula is a particularly interesting case
since the \(\sigma^2\) derived from the high-resolution dataset of the inner nebula on scales \(\approx \SI{0.1}{pc}\)
is roughly twice as large as that derived from the lower resolution
dataset of the Extended Orion Nebula on scales \(\approx \SI{1}{pc}\)
(compare panels a and b of Figure~\ref{fig:strucfunc-fit-Galactic}).
This is further evidence that the amplitude of velocity fluctuations
increases towards the center of the nebula in this source.

In contrast, other regions,
such as the Lagoon and NGC~346,
show \(B(r)\) increasing at the largest separations,
reaching values significantly larger than \(2\sigma^2\).
This can be evidence for a large-scale linear velocity gradient
across the region (see Figure~13 of \citealp{arthur2016turbulence})
or a periodic fluctuation with \(\lambda > r_0\)
(see section~\ref{sec:limit-model-struct} above).
This latter effect may also explain the behavior of NGC~604,
which shows oscillatory behavior of \(B(r)\),
similar to the light blue line in Figure~\ref{fig:model-strucfunc}b.

@@

In the section \ref{sec:results} we showed that each \hii{} region of our sample has a turbulent velocity field that can be characterized using the turbulence methods despite the results not being as the Kolmogorov model predicts.
The turbulent parameters obtained are unique to each velocity field.
We proceed to develop scaling relations between them and also between the physical properties of each region.

%Intro for scaling relations
Relationship between the physical properties of \hii{} regions, like size and luminosity, and the velocity dispersion have been used as tools for concluding scaling relations for these objects.
These relations have also been studied in dwarf galaxies and high-redshift star formation regions.
\citet{melnick1977,terlevich1981} were the first to shown an empirical relationship between the line width and the integrated properties of the \hii{} regions as the diameter or the luminosity ($r \sim \sigma ^{\sim 2}$ ; $\text{L}_{\text{H}} \sim \sigma ^{\sim 4}$).
They conclude that GEHRs follow this relation because they behave as self-gravitatory systems like globular clusters or elliptical galaxies.
The work of \citet{1988A&A...201..199A} confirmed these relationships considering the discrepancies of previous investigations obtaining \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.9}\) and \(r \propto \sigma^{1.84}\).
%\citet{1981MNRAS.194..809L}

%Previous research on scaling relations
\citet{2012MNRAS.422.3339W} have found that clumps and \hii{} regions follow scaling relations over the range of z = 0-2 for \halpha\ size, velocity dispersion, luminosity and mass, finding \(\sigma \propto r^{0.42}\), \(\text{L}_{\text{H}_{\alpha}} \propto r^{2.72}\) and \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4.18}\), respectively. 
This results imply that the same process are seen at high redshifts and the current epoch in star forming regions.
Recently, \citet{Moiseev:2015a} found that the relation in dwarf galaxies is \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{5}\).
\citet{2018MNRAS.474.1250F} presented the relationship between integrated H$_{\beta}$ line luminosity and the velocity dispersion for new data of 36 giant HII regions obtaining \(\text{L}_{\text{H}_{\beta}} \propto \sigma^{5.02 \pm 0.21}\).

%methods for our analysis
We follow through this analysis using the scaling relation as a research tool between the properties of the sample of HII regions and our results. 
We use the properties in Table \ref{tab:regions-properties} with the turbulent parameters in Table \ref{tab:Res} as the dependent variable to adjust a fit in the form \(Y = aX +b\). 
For this procedure we use a hierarchical Bayesian approach using the package \textit{linmix} \citep{2007ApJ...665.1489K}.
The results are shown in Table \ref{tab:RestStats} in ascending order for the p-value.
In the Figures \ref{fig:sigvsl} and \ref{fig:rvsR} we show the correlations with a significance level  $p < $0.05.
In all the figures the slope of the fit shown in solid black line is the mean of all red lines that reflect the posterior of the Bayessian analysis.

@@

>>>>

\newcommand\hii{\ion{H}{2}}
\newcommand\pos{\ensuremath{_{\mathrm{pos}}}}
\newcommand\los{\ensuremath{_{\mathrm{los}}}}
\newcommand\noise{\ensuremath{_{\text{noise}}}}
\newcommand\obs{\ensuremath{_{\mathrm{obs}}}}
\newcommand\model{\ensuremath{_{\mathrm{mod}}}}
\newcommand\halpha{H${\alpha}$}
\newcommand\n{[\ion{N}{II}]$\lambda$6584}
\newcommand\oi{[\ion{O}{III}]$\lambda$5007}
\newcommand\s{[\ion{S}{II}]$\lambda$6737}
\newcommand\kms{$^{-1}$}

@@

In order to capture these two behaviors,
We therefore propose the following idealized 2-parameter model
for the autocorrelation function:
%
\begin{equation}\label{eq:new-correlation-form}
  C\model(r;\ r_0, m) = 2^{- \left( r/r_0 \right)^m} 
\end{equation}
%
in which \(r_{0}\)\ is the correlation length (see above)
and \(m\) is the power-law slope at small scales.
This is constructed so that \(C\model(r) = 1/2\) at \(r = r_0\),
while the exponential form ensures that \(C(r)\) rapidly approaches zero
for larger separations.
We assume the validity of equation~\eqref{eq:functional} to determine the structure function
from this model autocorrelation function:
\begin{equation}
  \label{eq:model-strucfunc-ideal}
  B\model(r) = 2\sigma^2\pos \left[
    1 - 2^{- \left( r/r_0 \right)^m} 
  \right]
\end{equation}
This has the following properties:
\begin{enumerate}[1.]
 \item Small scales: \(B\model(r) \propto r^m\) for \(r \ll r_0\);
 \item Correlation scale: \(B\model(r_0) = \sigma\pos^2\);
 \item Large scales: \(B\model(r) \to 2 \sigma\pos^2\) for \(r \gg r_0\).
 \end{enumerate}
An example is shown by the blue line in Figure~\ref{fig:model-strucfunc}a.

@@

Combining both the effects of seeing and noise yields the corrected
model structure function:
\begin{equation}
  \tilde{B}\model(r) = B\model(r) \,  S(r) + B\noise
  \label{eq:sf-functional}
\end{equation}
An example of this equation is shown by the red line in Figure~\ref{fig:model-strucfunc}.
Note that seeing and noise have opposite effects on the slope
of the structure function at intermediate scales:
seeing tends to steepen the slope, while noise tends to flatten it.
This can lead to a degeneracy between these two parameters
when fitting observations over a limited range of separations.

@@

\begin{table}
  \centering
  \caption{Bounds of allowed values for parameters in model fits}
  \label{tab:parameter-ranges}
  \newlength\partabwidth
  \setlength\partabwidth{0.8\linewidth}
  \begin{tabular*}{\partabwidth}{
    l @{\extracolsep{\fill}}
    r 
    r
    }
    \toprule
    Parameter & Lower & Upper\\
    \midrule
    \(\sigma^2\) & \(0.25\, \max [B\obs]\)& \(2\, \max [B\obs]\)\\
    \(r_0\) & \(0.01\, L\) & \(2\, L\)\\
    \(m\) & \(0.5\) & \(2.0\) \\
    \(s_0\) & \SI{0.1}{arcsec}& \SI{1.5}{arcsec}\\
    \(B\noise\) & \(0\) & \(3\, \min [B\obs]\) \\
    \bottomrule
    \multicolumn{3}{@{}p{\partabwidth}@{}}{
    Note: \(\max[B\obs]\) and \(\min[B\obs]\) are over all bins in the observed structure function with \(r < L/2\).
    }
  \end{tabular*}
\end{table}

@@

In order to provide a uniform description of the velocity fluctuations,
we fit the model structure function
\(\tilde{B}\mod(r)\) of equation~\eqref{eq:sf-functional}
to each \hii{} region in our sample.
Results are shown in Figures~\ref{fig:strucfunc-fit-Galactic}, \ref{fig:strucfunc-fit-MC},
and~\ref{fig:strucfunc-fit-ExtraGal}, arranged in order of increasing distance.
Best-fit values for the model parameters,
together with 95\% credibility range,
are given in Table~\ref{tab:Res}.
After describing the methods used to
measure the structure function and fit the model (section~\ref{sec:techn-deta-model}),
we give details of the results in the example case of
the inner Orion Nebula (\ref{sec:example-results-orion})
and a broad overview of the results for other regions (\ref{sec:results-model-fitt}).
Further details of the results for individual regions are
given in Appendix~\ref{sec:notes-individual-hii}.

@@

For the observational values (\(B\obs(r)\); blue symbols),
the structure function is the average value of equation~\eqref{eq:Br}
over all pairs of points that contribute to each radial bin.
The uncertainty of each bin (blue error bars) is estimated
as the standard deviation of these values divided by the square root of
the number of contributing pairs.
\textit{But this is not true -- we use constant fractional error with adjustments for small and large separations.}
For most sources a fixed bin size of \SI{0.05}{dex} is used,
but for those observed with multi-fiber spectroscopy
(Carina and M8, see section~\ref{sec:flames-multi-fiber}),
where coverage is sparse at small separations,
adjacent bins were merged to ensure at least 100 pairs contribute to each bin.
Bins with separation less than \(L/2\) are used to constrain the model fitting (filled symbols),
while larger separations (open symbols) are not used
since they are more likely to be affected by a breakdown
of the homogeneity assumption (see section~\ref{sec:limit-model-struct}).
%This \(L/2\) constrain is not used for the regions observed with MUSE.

Non-linear weighted least square fitting of the model is performed
using the Levenberg-Marquardt algorithm \citep{More:1978a} as implemented in the
\texttt{lmfit} Python library \citep{newville_matthew_2014_11813}.
The best-fit model \(\tilde{B}\model(r)\) is shown (heavy orange solid line),
together with the corresponding underlying ``true model'' \(B\model(r)\) (heavy dashed green line),
which does not include the effects of seeing or noise.
Note that the true model \(B\model(r)\) depends on only 3 parameters:
\(\sigma^2\), \(r_0\), and \(m\),
whereas \(\tilde{B}\model(r)\) additionally depends on
the observational nuisance parameters: \(s_0\) and \(B\noise\).
The best-fit values of each of these parameters are shown by
horizontal and vertical lines in the figure and are summarised in Table~\ref{tab:Res}.

The posterior distributions of model parameters
that are consistent with the observations for each region are estimated
using Markov Chain Monte Carlo (MCMC) ensemble sampling \citep{2010CAMCS...5...65G}
as implemented in the \texttt{emcee} Python library \citep{2013PASP..125..306F}.
A uniform prior distribution is assumed between upper and lower bounds
for each parameter, as given in Table~\ref{tab:parameter-ranges}.
To help ensure convergence of the MCMC algorithm,
we used chain lengths that exceeded \num{50} times the
estimated autocorrelation length for each parameter,
which typically required of order \num{50000} samples.
Thin translucent lines in the figures show structure functions using the parameters of
a random selection of \num{100} posterior samples from the MCMC chain,
both for \(\tilde{B}\model(r)\) orange and \(B\model(r)\) (green).
This gives an estimate in the uncertainty about the best-fit model.
Credibility intervals for the parameters are estimated from percentiles
of the posterior distribution and are indicated in the figures by shaded gray boxes
around the best-fit parameter values
(heavy shading for 68\% interval; light shading for 95\% interval).
The 95\% credibility interval for each parameter and for each source
is also given in Table~\ref{tab:Res}.
Figure~\ref{fig:corner-example-Orion} gives an example for Orion of
the pairwise correlations in the posterior distributions of the model parameters,
plotted using the \texttt{corner} Python library \citep{2017ascl.soft02002F}.
Corresponding plots for the remaining sources and a table for the fitting parameters are given in Appendix~\ref{sec:addit-covar-corn}.

@@

The structure functions for sources in the Magellanic Clouds are shown in Figure~\ref{fig:strucfunc-fit-MC}
and those in more distant galaxies in Figure~\ref{fig:strucfunc-fit-ExtraGal}.
The Magellanic cloud sources have generally high data quality due to the
large number of independent spatial points in the MUSE observations
(section~\ref{sec:muse-integral-field}).
The relatively poor spectral resolution means that the \(B\obs(r)\) cannot
be measured down to such low values as in the inner Orion Nebula,
but the larger amplitude of the fluctuations in these sources means
that the fitted model parameters are still tightly constrained.

@@

The inner Orion Nebula has the largest inferred seeing FWHM of \SI{2.4(4)}{arcsec},
which is at least two times higher than the typical seeing measured during the observations
\citep{Doi:2004a}.
However, this can be at least partially explained by the fact that the velocity map is constructed
by interpolating individual longslit observations onto a regular grid
(section~\ref{sec:longsl-echelle-spect}).
The seeing-limited resolution will only be achieved along the slits,
whereas the resolution in the perpendicular direction is determined by the slit spacing of \SI{2}{arcsec}.
Given, this the model-derived value of \(s_0\) for this source is reasonable.

@@

At scales larger than \(L/2\),
we see a variety of different shapes for the structure functions
of our sample regions. 
In some cases,
such as Carina and Hubble~X,
\(B\obs(r)\) remains flat at a value of \(\approx 2\sigma^2\pos\),
which is consistent with uncorrelated homogeneous fluctuations
at the largest scales.

For other regions,
such as the Orion Nebula (both inner and outer) and 30~Doradus,
there is a clear downturn in \(B\obs(r)\) at the largest separations.
As discussed above in section~\ref{sec:limit-model-struct},
this is what would be expected if the velocity fluctuations
were inhomogeneous, with a larger amplitude in the center of the map
and a smaller amplitude in the outskirts.
A similar behavior, although not so marked, is shown by
Hubble~V and NGC~595.
The Orion Nebula is a particularly interesting case
since the \(\sigma^2\pos\) derived from the high-resolution dataset of the inner nebula on scales \(\approx \SI{0.1}{pc}\)
is roughly twice as large as that derived from the lower resolution
dataset of the Extended Orion Nebula on scales \(\approx \SI{1}{pc}\)
(compare panels a and b of Figure~\ref{fig:strucfunc-fit-Galactic}).
This is further evidence that the amplitude of velocity fluctuations
increases towards the center of the nebula in this source.

In contrast, other regions,
such as the Lagoon and NGC~346,
show \(B\obs(r)\) increasing at the largest separations,
reaching values significantly larger than \(2\sigma^2\pos\).
This can be evidence for a large-scale linear velocity gradient
across the region (see Figure~13 of \citealp{arthur2016turbulence})
or a periodic fluctuation with \(\lambda > r_0\)
(see section~\ref{sec:limit-model-struct} above).
This latter effect may also explain the behavior of NGC~604,
which shows oscillatory behavior of \(B\obs(r)\),
similar to the light blue line in Figure~\ref{fig:model-strucfunc}b.

@@

In section \ref{sec:results} we show that each velocity field of our sample can be characterized by parameters that are particular for each \hii{} region.
We used these parameters to develop scaling relations between them and the physical properties of each region.

%Intro for scaling relations
Correlations between the physical properties of \hii{} regions like size, luminosity, and the velocity dispersion have been used as tools for finding scaling relationships for these objects.
These kind of relations have also been found in dwarf galaxies and high-redshift star formation regions.
\citet{melnick1977,terlevich1981} were the first to shown an empirical relationship between the line width and the integrated properties of the \hii{} regions as the diameter or the luminosity (\(r \sim \sigma ^{\sim 2}\) ; \(\text{L}_{\text{H}} \sim \sigma ^{\sim 4}\)).
In later years, \citet{1988A&A...201..199A} confirmed these relationships considering the discrepancies of previous investigations obtaining \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.9}\) and \(r \propto \sigma^{1.84}\).
%\citet{1981MNRAS.194..809L}
In recent years, \citet{2012MNRAS.422.3339W} have found that clumps and \hii{} regions follow scaling relations over the range of z = 0-2 for \halpha\ size, velocity dispersion, luminosity and mass, finding \(\sigma \propto r^{0.42}\), \(\text{L}_{\text{H}_{\alpha}} \propto r^{2.72}\) and \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4.18}\), respectively. 
This results imply that the same process are seen at high redshifts and the current epoch in star forming regions.
Recently, \citet{Moiseev:2015a} found that the relation in dwarf galaxies is \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{5}\).
\citet{2018MNRAS.474.1250F} presented the relationship between integrated H$_{\beta}$ line luminosity and the velocity dispersion for new data of 36 giant HII regions obtaining \(\text{L}_{\text{H}_{\beta}} \propto \sigma^{5.02 \pm 0.21}\).

%methods for our analysis

We implement a hierarchical Bayesian model for fitting a straight line using the \texttt{linmix} Python library based on \cite{2007ApJ...665.1489K}.
The physical properties in Table \ref{tab:regions-properties} are the independent variable \(X\) and the turbulent parameters in Table \ref{tab:Res} are the dependent variable \(Y\). 
The results are shown in Table \ref{tab:RestStats} in ascending order for the p-value.
In the Figures \ref{fig:sigvsl} and \ref{fig:rvsR} we show the correlations with a significance level \(p < \num{0.05}\).
The black solid line shows the input regression line and the red lines show some samples from the posterior distribution.

@@

As for the power-law index \(m\) we can see from table \ref{tab:RestStats} that this parameter does not correlate with any other parameter or physical property.
